% -- Encoding UTF-8 without BOM
% -- XeLaTeX => PDF (BIBER)

\documentclass[]{cv-style}          % Add 'print' as an option into the square bracket to remove colours from this template for printing. 
                                    % Add 'espanol' as an option into the square bracket to change the date format of the Last Updated Text

\sethyphenation[variant=british]{english}{} % Add words between the {} to avoid them to be cut 

\usepackage{hyperref}

\begin{document}


\headerwithjob{Carlos}{Alcala}{Front End Developer  \& Game Designer}          % Your name

\lastupdated

%----------------------------------------------------------------------------------------
%	SIDEBAR SECTION  -- In the aside, each new line forces a line break
%----------------------------------------------------------------------------------------

\begin{aside}
%
\section{contact}
+52 (449) 222 1912
~
\href{mailto:Solenasthellion
@gmail.com}{Solenasthellion
@gmail.com}
~-
\href{https://github.com/Solenasth/}{github.com
/Solenasth}
%
\section{languages}
Bilingual English
Native Spanish
%
\section{programming}
{\color{red} $\varheartsuit$} Javascript ES6
SASS, Html 5
OOP (C\#)
DB - Relational \& Non-Relational
\section{game dev}
{\color{red} $\varheartsuit$} Game Design
Gamification
User Psychology
\section{in training}
{\color{red} $\varheartsuit$} Firebase
React
Rest Microservices
\section{top gallup Strenghts}
(click on any for more information)
~-
\href{https://news.gallup.com/businessjournal/718/strategic.aspx}{Strategic}
\href{https://news.gallup.com/businessjournal/685/individualization.aspx}{Individualization}
\href{https://news.gallup.com/businessjournal/625/activator.aspx}{Activator}
\href{https://news.gallup.com/businessjournal/679/ideation.aspx}{Ideation}
\href{https://news.gallup.com/businessjournal/622/achiever.aspx}{Achiever}
%
\section{project summary}
{\color{red} $\varheartsuit$} \href{https://docs.google.com/document/d/1Aj6Jy7RefQvkJJ9pEEydWflzKYrMHOWXZvgLfn9VK6s/edit?usp=sharing}{(click here for a quick summary of some of my projects and conferences)}
\end{aside}

%----------------------------------------------------------------------------------------
%	SKILLS SECTION
%----------------------------------------------------------------------------------------

\section{about}
  \vspace{-0.2cm}
Excellent communication skills. Agile Development. Adaptability. Multidisciplinary Team Player. Public Speaking. UX Design Proficient. Strong understanding of user psychology. Results driven. disposition for learning and high capability for mastery.


%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\section{experience}


\begin{entrylist}
%------------------------------------------------
\entry
  {2017--Now}
  {ACCENTURE}
  {Monterrey, Mexico}
  {\jobtitle{User Experience Engineer(Front End)}\\
 I have worked under heavy security regulations for a client in the health industry, my main tasks include ensuring consistency between CMS-produced assets and UX guidelines, improve asset build process for the client, and do research and development of new ways to improve the work pipeline. During my spare time I worked on internal projects researching and prototyping applications in Firebase }
%------------------------------------------------
\entry
  {2015--2017}
  {STAR JELLY GAMES}
  {Aguascalientes, Mexico}
  {\jobtitle{Team lead, Art director, Scrum Master}\\
  This was my start-up, we developed games and general software, mostly focusing on our strengths to create interactive web experiences, during this time I learned a lot about project management and multidisciplinary teams, each of us had to wear many hats, and mine mostly focused on team leading, game design and art direction. }
%------------------------------------------------
\entry
  {2013--2017}
  {ANIMACTIVA}
  {Aguascalientes, Mexico}
  {\jobtitle{Outsourced Tech Advisor and developer}\\
  We incubated our start up in Animactiva, during that time I regularly served as a tech advisor and developer for several projects with them, my main tasks included evaluating client needs and proposing a clear path for success, estimate efforts and development times for the team and communicate that information to the client.
}
%------------------------------------------------

\end{entrylist}

%----------------------------------------------------------------------------------------
%	CONFERENCES AND WORKSHOPS SECTION
%----------------------------------------------------------------------------------------
%
%\section{imparted conferences and courses}
%
%\begin{entrylist}
%------------------------------------------------
%\entry
%{2010--2014}
%{B.Eng. {\normalfont Computer Systems Engineer }}
%{Universidad Autonoma de Aguascalientes}
%{\vspace{-0.3cm}}
%
%------------------------------------------------
%\end{entrylist}




%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\section{education}

\begin{entrylist}
%------------------------------------------------
\entry
{2010--2014}
{B.Eng. {\normalfont Computer Systems Engineer (equivalent to Computer Science Engineering) }}
{Universidad Autonoma de Aguascalientes}
{\vspace{-0.3cm}}

%------------------------------------------------
\end{entrylist}




%----------------------------------------------------------------------------------------
%	CONFERENCES SECTION
%----------------------------------------------------------------------------------------

\section{Conferences \& Workshops}

\begin{entrylist}
%------------------------------------------------
\entry
{2016}
{{\normalfont Game Design and how to start developing games }}
{Aguascalientes}
{\vspace{-0.3cm}}
\entry
{2015}
{{\normalfont Gamification \& its impact in User eXperience }}
{DevHr \& Campus Party }
{\vspace{-0.3cm}}
\entry
{2013 , 2014}
{{\normalfont Game development, State of the industry and how to start }}
{Aguascalientes}
{\vspace{-0.3cm}}

%------------------------------------------------
\end{entrylist}





%----------------------------------------------------------------------------------------
%	INTERESTS SECTION
%----------------------------------------------------------------------------------------

\section{interests}
  \vspace{-0.4cm}

\textbf{professional:} {Game Development, Game Design, Web Technologies, Serverless architecture, Javascript frameworks.} 

\textbf{personal:} {Videogames, Tea blends, Lo-Fi beats, Creative Writing, Dogs, Dungeons \& Dragons}

%----------------------------------------------------------------------------------------

\end{document}